A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex
Reduce wording

% remove? - vhs
The reduce is done differently for the engines. Spark and Delayed compute
all the reduce tasks on one process (thread), however, Spark only computes it
on the driver process. On the other hand, Bag computes the reduce tasks on 
different workers and sends the information to the driver process afterward.

@@

Varying the block size or the size of the partitions is equivalent. No difference is
observed when varying the task size while using an NFS. However, if one uses a
parallel shared file system, we suppose it would be preferable to use a larger block
size as the IO time should be reduced substantially. It is worth noting that the Dask
developers suggest, in
\href{https://docs.dask.org/en/latest/best-practices.html}{Dask's best practices}, to
use a partition size such that workers have 2-3 times as many chunks available to
work on. More experiments would have to be performed to gain insight on an optimal
number of partitions to use for a given set of data-intensive applications.

>>>>

% % remove? - vhs
% The reduce is done differently for the engines. Spark and Delayed compute
% all the reduce tasks on one process (thread), however, Spark only computes it
% on the driver process. On the other hand, Bag computes the reduce tasks on 
% different workers and sends the information to the driver process afterward.

@@

Varying the block size or the size of the partitions is equivalent. No difference is
observed when varying the task size while using an NFS. However, if one uses a
parallel shared file system, it would be preferable to use a larger block
size as the IO time should be reduced substantially. It is worth noting that the Dask
developers suggest, in
\href{https://docs.dask.org/en/latest/best-practices.html}{Dask's best practices}, to
use a partition size such that workers have 2-3 times as many chunks available to
work on. More experiments would have to be performed to gain insight on an optimal
number of partitions to use for a given set of data-intensive applications.
